Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.

### 2015-05-03 papers/MbhMsph/mm.tex
s

\begin{abstract}
We present correlations between black hole mass, $M_{\rm BH}$, 
and both the host galaxy's and spheroid's infrared luminosity, $L_{\rm gal}$ and $L_{\rm sph}$, 
and the spheroid's stellar mass, $M_{\rm *,sph}$,
built upon a high-quality data set.
Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
%Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
%which is minimally affected by dust and star formation. 
%These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
%that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
%and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
and were derived from our state-of-the-art multicomponent galaxy decompositions 
that, for the first time, were checked to be consistent with the galaxy kinematics. 
{\bf limit of 250 words, no room for mentioning the gaalxy components, more appropriate for data paper}
Previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
%We provide updated linear regressions 
%(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
%for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

used similar galaxy samples, which remained dominated by high-mass, early-type objects having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 

@@

and reported a slope below unity for their $M_{\rm BH} - M_{\rm sph}$ relation. 

@@

The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two correlations involving the bulge velocity dispersion, $\sigma$.

@@

which can be described by a single power-law ($M_{\rm BH} \propto \sigma^5$) 
over the range in velocity dispersion $70-350~\rm km~s^{-1}$ (e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).

@@

and attributed the change in slope (from log-quadratic to log-linear) to their different formation mechanisms. 

@@

\citeauthor{grahamscott2013} (\citeyear{grahamscott2013}, hereafter GS13) and \citeauthor{scott2013} (\citeyear{scott2013}, hereafter S+13) 

@@

for S\'ersic/core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
(spheroid stellar mass) diagrams, respectively, probing down to $M_{\rm BH} \approx 10^6\rm~M_\odot$. 

@@

However, this mean statistical correction was obtained from the results of non-modern bulge/disk decompositions, 
which did not include extra components. 

@@

are not randomly offset from the high-mass, near-linear correlation, 

@@

discuss how we estimated the uncertainties\footnote{By comparing, for our galaxies, the measurements of the bulge magnitude 
obtained by different authors with those obtained by us, we estimated the uncertainties on the bulge magnitudes 

@@

\section{Analysis}
\label{sec:anal}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}),
using the BCES code from \cite{akritasbershady1996}. 
We also repeated the analysis with the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
All these three linear regression routines account for the intrinsic scatter, 
but only the last two allow to quantify it.
%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
We report linear regressions, both symmetrical and non-symmetrical, 
for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas non-symmetrical $(Y|X)$ regressions -- 
since they minimize the scatter in the vertical direction -- 
can be used to predict black hole masses.

@@

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ log-correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ log-correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ log-relations have the same level of intrinsic scatter. 
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the uncertainties associated to the luminosities\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
We decided to vary only the errors associated to $L_{\rm gal}$ 
because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
that takes into account the systematic errors related to the galaxy decomposition process. 
We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ log-relations for early-type galaxies 
have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
we conclude that our determination of the intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing accurate galaxy decompositions to obtain bulge luminosities. 
This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

@@

is consistent with the slope reported by GS13 in the $K_s$-band ($M_{\rm BH} \propto L_{\rm sph}^{1.10 \pm 0.20}$). 

@@

We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ log-correlation -- 

@@

\subsection{Pseudo- versus classical bulges}
Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
formed through violent processes, such as hierarchical clustering via minor mergers, 
and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
thus rotation is not a definitive signature of a pseudobulge. 
Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
macarthur2009,dosanjosdasilva2013,seidel2015}). 
In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{sani2011,beifiori2012}), 
although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
being disky components that formed from their surrounding exponential disks 
(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
it has been shown that mergers can create bulges with $n_{\rm sph}<2$
(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
traced by classical bulges. 
In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
in the $M_{\rm BH} - L_{\rm sph}$ diagram.
Our aim is to check whether $n_{\rm sph}<2$ bulges 
are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
and we compute the vertical offset of all bulges from the regression. 
In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
Among the 23 bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset. 
\cite{kormendy2015review} provides a list of many pseudo-bulges classification criteria, including the divide at $n_{\rm sph}=2$, 
and cautions that each individual criterion has a failure rate of 0-25\% \citep{fisherdrory2015}. 
If this is true, we should have that no less than 75\% of $n_{\rm sph}<2$ bulges have negative vertical offset. 
What we observe, instead, is that there are the same number of $n_{\rm sph}<2$ bulges lying above and below 
the correlation defined by $n_{\rm sph}>2$ bulges\footnote{One 
reaches the same conclusion when using the vertical offset from the correlation defined by bulges with $n_{\rm sph}>3$. 
In this case, there are 13 and 10 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation of $n_{\rm sph}>3$ bulges.}, 
and that the amplitude of their offset is the same ($\lesssim 1.5\rm~dex$).
That is, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.

@@

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
and its linear regression analysis in Table \ref{tab:lregmass}. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
whose slope is less well constrained due to the small size of the subsample and, more importantly, 
to the small range in $M_{\rm *,sph}$ that the subsample spans. 
More data would be welcome to better constrain the slope of this \emph{blue sequence}.
For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $3.00 \pm 1.30$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
slope $2.28^{+1.67}_{-1.01}$.
The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies.

\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting Active Galactic Nuclei (AGNs) with 
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges. 
%Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
We anticipate here that the correlation traced by our bulges of spiral galaxies 
may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
That is, the AGNs appear to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.
This topic will be investigated in Graham et al. (2015, \emph{in preparation}) with a dedicated careful analysis. \\

>>>>

\begin{abstract}
We present correlations between black hole mass, $M_{\rm BH}$, 
and both the host galaxy's and spheroid's infrared luminosity, $L_{\rm gal}$ and $L_{\rm sph}$, 
and the spheroid's stellar mass, $M_{\rm *,sph}$,
built upon a high-quality data set.
Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
%Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
%which is minimally affected by dust and star formation. 
%These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
%that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
%and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
and were derived from our state-of-the-art {\bf many-component} galaxy decompositions 
that, for the first time, were checked to be consistent with the galaxy kinematics. 
{\bf limit of 250 words, no room for mentioning the gaalxy components, more appropriate for data paper}
Previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
%We provide updated linear regressions 
%(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
%for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

used similar galaxy samples, which remained dominated by high-mass, early-type systems having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 

@@

and reported a slope below unity for their $M_{\rm BH} - L_{\rm sph}$ relation. 

@@

The $M_{\rm BH} - L_{\rm sph}$ relation can be predicted from other two correlations that involve 
the bulge stellar velocity dispersion, $\sigma$.

@@

which can be described with a single power-law ($M_{\rm BH} \propto \sigma^5$) 
over a wide range in velocity dispersion ($70-350~\rm km~s^{-1}$, e.g.~\citealt{graham2011,mcconnell2011,grahamscott2013}).

@@

and attributed the change in slope (from quadratic to linear) to their different formation mechanisms. 

@@

\citeauthor{grahamscott2013} (\citeyear{grahamscott2013}, hereafter GS13) and \citeauthor{scott2013} (\citeyear{scott2013}) 

@@

for S\'ersic and core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
(spheroid stellar mass) diagrams, probing down to $M_{\rm BH} \approx 10^6\rm~M_\odot$. 

@@

However, this mean statistical correction was obtained from the results of non-modern bulge/disk decompositions. 

@@

are not randomly offset from such near-linear correlation, 

@@

discuss how we estimated the uncertainties\footnote{By comparing, for each of our galaxies, the measurements of the bulge magnitude 
obtained by different authors with that obtained by us, we estimated the uncertainties on the bulge magnitudes 

@@

\section{Analysis}
\label{sec:anal}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}),
using the BCES code from \cite{akritasbershady1996}. 
We also repeated the analysis with the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
All these three linear regression routines account for the intrinsic scatter, 
but only the last two allow to quantify it.
%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
We report linear regressions, both symmetrical and non-symmetrical, 
for S\'ersic/core-S\'ersic and for early/late-type galaxies.
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas non-symmetrical $(Y|X)$ regressions -- 
since they minimize the scatter in the $\log M_{\rm BH}$ direction -- 
can be used to predict black hole masses.

@@

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the amplitude of the uncertainties associated to the luminosities\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
We decided to vary only the errors associated to $L_{\rm gal}$ 
because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
that takes into account the systematic errors related to the galaxy decomposition process. 
We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
we conclude that our determination of the intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing accurate galaxy decompositions to obtain bulge luminosities. 
This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

@@

is consistent with the slope reported by GS13 in the $K_s$-band for the same population ($M_{\rm BH} \propto L_{\rm sph}^{1.10 \pm 0.20}$). 

@@

We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 

@@

\subsection{Pseudo- versus classical bulges}
Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
formed through violent processes, such as hierarchical clustering via minor mergers, 
and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
thus rotation is not a definitive signature of a pseudobulge. 
Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
macarthur2009,dosanjosdasilva2013,seidel2015}). 
In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{sani2011,beifiori2012}), 
although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
being disky components that formed from their surrounding exponential disks 
(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
it has been shown that mergers can create bulges with $n_{\rm sph}<2$
(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
traced by classical bulges. 
In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic index 
is taken from our one-dimensional fit of the galaxy's major-axis surface brightness profile (\emph{Paper I}).} 
in the $M_{\rm BH} - L_{\rm sph}$ diagram.
Our aim is to check whether $n_{\rm sph}<2$ bulges 
are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
and we compute the vertical offset of all bulges from the regression. 
In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
Among the 23 bulges with $n_{\rm sph}<2$, 12 have positive vertical offset and 11 have negative vertical offset. 
\cite{kormendy2015review} provides a list of many pseudo-bulges classification criteria, including the divide at $n_{\rm sph}=2$, 
and cautions that each individual criterion has a failure rate of 0-25\% \citep{fisherdrory2015}. 
If this is true, we should have that no less than 75\% of $n_{\rm sph}<2$ bulges display negative vertical offset. 
What we observe, instead, is that there are the same number of $n_{\rm sph}<2$ bulges lying above and below 
the correlation defined by $n_{\rm sph}>2$ bulges\footnote{One 
reaches the same conclusion when using the vertical offset from the correlation defined by bulges with $n_{\rm sph}>3$. 
In this case, there are 13 and 10 bulges with $n_{\rm sph}<2$ that lie above and below, respectively, the correlation  
traced by $n_{\rm sph}>3$ bulges.}, 
and that the amplitude of their offset is the same ($\lesssim 1.5\rm~dex$).
That is, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.

@@

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
and its linear regression analysis in Table \ref{tab:lregmass}. 
The bulges of early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
On the other hand, the bulges of spiral galaxies trace a steeper \emph{blue sequence}, 
whose slope is less well constrained due to the small size of the subsample and, more importantly, 
to the small range in $M_{\rm *,sph}$ that the subsample spans. 
More data would be welcome to better constrain the slope of this \emph{blue sequence}.
For the bulges of spiral galaxies, the BCES code returns a log-linear relation with slope $= 3.00 \pm 1.30$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
slope $= 2.28^{+1.67}_{-1.01}$.
The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies.

\cite{grahamscott2015} collected a sample of $\sim$170 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting Active Galactic Nuclei (AGNs) with 
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 0.5 \times 10^8$, 
and showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by S\'ersic bulges. 
%Although we demonstrated that, using our dataset, the S\'ersic bulges do not define a quadratic relation, 
We anticipate here that the correlation traced by our bulges of spiral galaxies 
may track the location of the AGNs in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
That is, the AGNs appear to be the low-mass continuation of the \emph{blue sequence} shown in Figure \ref{fig:mbhmasssph}. 
We additionally note that the majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
(Nasa Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.}.
This topic will be investigated in Graham et al. (2015, \emph{in preparation}) with a dedicated careful analysis. \\
